Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-05-13 Thesis/chapter/05-computational-details.tex
add ML wikis

\subsection{Data Processing}
\label{sec:eval}
%\td{describe problem and solution found}
For every sample multiple \gls{iv} curves were measured. 
The main difficulty faced in processing the data was to present the measurements obtain 
from a sample in one representative number. 
The average of each conductance would be an obvious choice but difficult to represent a 
sample correctly since the possible values of conductance span accross several magnitudes.
So the average of logarithms of conductances is the next nearby ansatz.
\todo{why didn't i just take this?}
\td{L2 norm because it might be easier to compare to other methods. }
\td{inspired by euclidean norm/L2 distance from ideal case} 
\td{wanted to put more weight on bad shunts}
\td{plot avg, avg(log), avg(log-13)}

>>>>

\subsection{Data Processing}
\label{sec:eval}
Reading list
\begin{itemize}
    \item https://de.wikipedia.org/wiki/Globaler_F-Test
    \item https://de.wikipedia.org/wiki/Optimale_Versuchsplanung
    \item Curse of dimensionality scholar
    \item linear regression von ungar 
    \item ridge regression + support vector machine
    \item correlation vs covariance
    \item https://en.wikipedia.org/wiki/Regression_analysis
    \item https://en.wikipedia.org/wiki/Noise_reduction
    \item https://en.wikipedia.org/wiki/Feature_extraction
    \item https://en.wikipedia.org/wiki/Feature_selection
    \item https://en.wikipedia.org/wiki/Dimensionality_reduction
    \item file:///home/pur/Doc/Uni/Chemie_Master/Int_AIT/Int.git/Code/ML/98_things_can_go_wrong_in_ML_project.html
    \item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.PCA.html
    \item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.KernelPCA.html#sklearn.decomposition.KernelPCA
    \item 
    \item 
    \item 
\end{itemize}
%\td{describe problem and solution found}
For every sample multiple \gls{iv} curves were measured. 
The main difficulty faced in processing the data was to present the measurements obtain 
from a sample in one representative number. 
The average of each conductance would be an obvious choice but difficult to represent a 
sample correctly since the possible values of conductance span accross several magnitudes.
So the average of logarithms of conductances is the next nearby ansatz.
\todo{why didn't i just take this?}
\td{L2 norm because it might be easier to compare to other methods. }
\td{inspired by euclidean norm/L2 distance from ideal case} 
\td{wanted to put more weight on bad shunts}
\td{plot avg, avg(log), avg(log-13)}
